Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-01 article.tex
Change section 4.1 organisation and add some minor review

On top of these elements five processes are used: \emph{production}, \emph{consumption} \emph{cultural transmission}, \emph{innovation} and \emph{trade}. The \emph{production} process describes the creation of goods by the agent. Once a good is produced by an agent $i$ it is added to its quantity vector ($Q^i$). The consumption strategy of these goods is defined in the \emph{consumption} process. In this article, all goods are completely consumed at each iteration for all the models tested. The \emph{trade} process models the exchange of goods between the agents which results in a modification of the quantity vectors ($Q^i$). The amount of goods exchanged is computed by the agents involved in the trade, within the \emph{trade} process, based on their value vectors ($V^i$). Within the \emph{cultural transmission} process an agent $i$ can copy the entire value vector ($V^j$) of an agent $j$, where $j \neq i$. Finally, the \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultural transmission} process in that the modification is done without reference to the other agents.

@@

\paragraph{Production}
Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.

@@

\todo{check the numbers}
We first analyse the result obtained in the ``neutral model". Experiments have been performed for one, two and five goods. Unfortunately the presentation of the results for more than one good and multiple innovation probability would require a large space to be clear. For this reason, the figure~\ref{fig:allMutation} presents the results obtained in the setups using 1 good, two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064). The figure represents the average (across all the runs) of the distribution of variants obtained through all experiments. The y-axis shows the frequencies of the variants of the prices used during the simulation, the x-axis shows how many variant achieves such frequencies. Both axes are in a logarithmic scale. Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
\simon{Didn't get why there is mention of ``high frequency'' in the last sentence. I found this sentence a bit confusing }

@@

In order to verify if the distribution is in fact a power-law, we will follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and its R implementation done by~\cite{gillespie_fitting_2015}.

Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the function of power law equation $P(v)=C/v^\alpha $.
To estimate them we use maximum likelihood estimator and Kolmogorof-Smirnov approach. This method gives use an estimated $\alpha$ parameter that one can see in the table~\ref{tab:mualpha}.

@@

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[h]
	\centering
	\begin{tabular}{l|llll}
		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
		      & 1   & 3   &  6 & 9  \\\hline
		0.004 &1.53 (0.03)  &1.53 (0.03)&1.53 (0.03)&1.53 (0.03) \\
		0.016 &1.57 (0.02)  &1.57 (0.02)&1.57 (0.02)&1.57 (0.02) \\
		0.064 &1.66 (0.01)  &1.66 (0.01)&1.66 (0.01)&1.66 (0.01) \\\hline
	\end{tabular}
	\caption{Mean $\alpha$ and standard deviation for all innovation rate and different  of goods. The $\alpha$ given here is the mean $\alpha$ among all goods taken separately and computed over 100 runs with 250 agents.}
	\label{tab:multiGoods}
\end{table}

@@

In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``neutral model''. The figure~\ref{fig:2setDi}.a) presents the results obtained from 100 runs for each model. All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.

>>>>

On top of these elements five processes are used: \emph{production}, \emph{consumption}, \emph{cultural transmission}, \emph{innovation} and \emph{trade}. The \emph{production} process describes the creation of goods by the agent. Once a good is produced by an agent $i$ it is added to its quantity vector ($Q^i$). The consumption strategy of these goods is defined in the \emph{consumption} process. In this article, all goods are completely consumed at each iteration for all the models tested. The \emph{trade} process models the exchange of goods between the agents which results in a modification of the quantity vectors ($Q^i$). The amount of goods exchanged is computed by the agents involved in the trade, within the \emph{trade} process, based on their value vectors ($V^i$). Within the \emph{cultural transmission} process an agent $i$ can copy the entire value vector ($V^j$) of an agent $j$, where $j \neq i$. Finally, the \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultural transmission} process in that the modification is done without reference to the other agents.

@@

\paragraph{Production}
Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$. At each time step each agent produces $n$ units of its production good, which ensure that he could theoretically trade its production good with every other goods, with the particularity that when the agent consume is own production good he will automatically reproduce some in order that it won't impact is inventory.

@@

\todo{check the numbers}
We first analyse the result obtained in the ``neutral model". Following the literature, experiments have been performed for one good. The figure~\ref{fig:allMutation} presents the results obtained in for two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064). The figure represents the average (across all the runs) of the distribution of variants obtained through all experiments. The y-axis shows the frequencies of the variants of the prices used during the simulation, the x-axis shows how many variant achieves such frequencies. Both axes are in a logarithmic scale. Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
\simon{Didn't get why there is mention of ``high frequency'' in the last sentence. I found this sentence a bit confusing }

@@

In order to verify if the distribution is in fact a power-law, we follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and the R implementation of this method done by~\cite{gillespie_fitting_2015}.

Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
To estimate this the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach. It gives use an estimated $\alpha$ parameter that are summarized in the table~\ref{tab:mualpha}.

@@

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[h]
	\centering
	\begin{tabular}{l|llll}
		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
		      & 1   & 3   &  6 & 9  \\\hline
		0.004 &1.53 (0.03)  &1.53 (0.03)&1.53 (0.03)&1.53 (0.03) \\
		0.016 &1.57 (0.02)  &1.57 (0.02)&1.56 (0.017)&1.57 (0.02) \\
		0.064 &1.66 (0.01)  &1.66 (0.01)&1.66 (0.01)&1.66 (0.01) \\\hline
	\end{tabular}
	\caption{Mean $\alpha$ and standard deviation for all innovation rate and different  of goods. The $\alpha$ given here is the mean $\alpha$ among all goods taken separately and computed over 100 runs with 250 agents.}
	\label{tab:multiGoods}
\end{table}

\simon{Remainder here : we have a problem here as it's true that the number of goods does not impact the repartition of the price when vector are randomly exchange, \emph{it is not true} when the vector are  }

@@

In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``neutral model''. The figure~\ref{fig:2setDi}.a) presents the results obtained from 100 runs for each model. All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004. In all following graph  a variant is one price for one given good. All goods are thus studied independently.
